A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-28 5_generalization.tex
make all constants a part of the beading scheme

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of parameters and functions:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), B(n, d) \right\},
$$
where, as introduced in previous section, $\alpha_{\text{max}}$ is the limit bisector angle,
$q(d)$ the quantization operator,
$t(n)$ the transition length,
$t_0(n)$ the transition anchor position
and
$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$.
%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item For toolpaths to be smooth we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
\begin{array}{rlrl}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}    &    t_\text{beading} &= w^* \\
d_\text{max}^\text{unmarked} &= w^*    &    t(n) &= w^*  \\ 
d^\text{discretization} &= \SI{0.2}{\milli\meter}    &    t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent}     &     \alpha_\text{max} &= \SI{135}{\degree} \\
\end{array} \\
%\end{align*}
%\begin{align*}
L(n,d)_i = 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures thatwe don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.

>>>>

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of functions and constants:
\begin{align*}
\{
&q(d),
B(n, d),
t(n),
t_0(n),
\\
&\alpha_\text{max}, 
t_\text{beading}, 
d_\text{max}^\text{transition}, 
d_\text{max}^\text{unmarked}, 
d_\text{max}^\text{intersection},
d^\text{discretization}
 \}
\end{align*}
where, as introduced in previous section,
$q(d)$ the quantization operator,
$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$,
$t(n)$ the transition length,
$t_0(n)$ the transition anchor position,
$\alpha_{\text{max}}$ is the limit bisector angle,
$t_\text{beading}$ is the beading conflict transition length,
$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
and
$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
L(n,d)_i = 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\\
\begin{array}{rlrl}
t_\text{beading} &= w^* 
&
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
\\
t(n) &= w^*
&
d_\text{max}^\text{unmarked} &= w^*
\\
t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
&
d^\text{discretization} &= \SI{0.2}{\milli\meter}
\\
\alpha_\text{max} &= \SI{135}{\degree} 
&
d_\text{max}^\text{intersection} &= \SI{75}{\percent}
\end{array}
%\end{align*}
%\begin{align*}
\end{align*}

The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.
The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
